### 2017-12-12 submission/manuscript.Rmd
update methods with Gohl reference

***PCR Protocol:***
The five different high fidelity (HiFi) Taq DNA polymerase that were tested were AccuPrime^TM^ (ThermoFisher, MA, USA), KAPA HIFI (Roche, IN, USA), Phusion (ThermoFisher, MA, USA), Platinum (ThermoFisher, MA, USA), and Q5 (New England Biolabs, MA, USA). The PCR cycle conditions were the same for every primer [@protocol_Kozich_2013] (https://github.com/SchlossLab/MiSeq_WetLab_SOP/blob/master/MiSeq_WetLab_SOP_v4.md). If the HiFi Taq had a specific activation time that was different then 2 minutes that was used instead. The 30 cycle default was used but the cycle conditions started at 15 and increased by 5 up to 35 cycles and was used for both fecal and mock samples. The fecal PCR consisted of all 4 samples at 15, 20, 25, 30, and 35 cycles for each Taq (total samples = 100). Although, the mock communities also had 4 replicates used for 15, 20, 25, and 35 cycles, 10 replicates were used for 30 cycles for all Taq (total samples = 130). For all the mock community samples there was not enough PCR product at 15 cycles for adequate sequencing.

>>>>

***PCR Protocol:***
The five different high fidelity (HiFi) Taq DNA polymerase that were tested were AccuPrime^TM^ (ThermoFisher, MA, USA), KAPA HIFI (Roche, IN, USA), Phusion (ThermoFisher, MA, USA), Platinum (ThermoFisher, MA, USA), and Q5 (New England Biolabs, MA, USA). The PCR cycle conditions for Platinum and Accuprime followed a previously published protocol [@protocol_Kozich_2013] (https://github.com/SchlossLab/MiSeq_WetLab_SOP/blob/master/MiSeq_WetLab_SOP_v4.md). If the HiFi Taq had a specific activation time that was different then 2 minutes that was used instead. For Kappa and Q5 the protocol previously published by Gohl and colleagues was used [@taq_Gohl_2016]. For Phusion the company defined conditions were used but the same extension time as that used for Accuprime and Platinum was used.

The 30 cycle default was used but the cycle conditions started at 15 and increased by 5 up to 35 cycles and was used for both fecal and mock samples. The fecal PCR consisted of all 4 samples at 15, 20, 25, 30, and 35 cycles for each Taq (total samples = 100). Although, the mock communities also had 4 replicates used for 15, 20, 25, and 35 cycles, 10 replicates were used for 30 cycles for all Taq (total samples = 130). For all the mock community samples there was not enough PCR product at 15 cycles for adequate sequencing.

### 2017-12-12 submission/manuscript.tex
update methods with Gohl reference

\textbf{\emph{PCR Protocol:}} The five different high fidelity (HiFi)
Taq DNA polymerase that were tested were AccuPrime\textsuperscript{TM}
(ThermoFisher, MA, USA), KAPA HIFI (Roche, IN, USA), Phusion
(ThermoFisher, MA, USA), Platinum (ThermoFisher, MA, USA), and Q5 (New
England Biolabs, MA, USA). The PCR cycle conditions were the same for
every primer (Kozich et al., 2013)
(\url{https://github.com/SchlossLab/MiSeq_WetLab_SOP/blob/master/MiSeq_WetLab_SOP_v4.md}).
If the HiFi Taq had a specific activation time that was different then 2
minutes that was used instead. The 30 cycle default was used but the
cycle conditions started at 15 and increased by 5 up to 35 cycles and
was used for both fecal and mock samples. The fecal PCR consisted of all
4 samples at 15, 20, 25, 30, and 35 cycles for each Taq (total samples =
100). Although, the mock communities also had 4 replicates used for 15,
20, 25, and 35 cycles, 10 replicates were used for 30 cycles for all Taq
(total samples = 130). For all the mock community samples there was not
enough PCR product at 15 cycles for adequate sequencing.

@@

>>>>

\textbf{\emph{PCR Protocol:}} The five different high fidelity (HiFi)
Taq DNA polymerase that were tested were AccuPrime\textsuperscript{TM}
(ThermoFisher, MA, USA), KAPA HIFI (Roche, IN, USA), Phusion
(ThermoFisher, MA, USA), Platinum (ThermoFisher, MA, USA), and Q5 (New
England Biolabs, MA, USA). The PCR cycle conditions for Platinum and
Accuprime followed a previously published protocol (Kozich et al., 2013)
(\url{https://github.com/SchlossLab/MiSeq_WetLab_SOP/blob/master/MiSeq_WetLab_SOP_v4.md}).
If the HiFi Taq had a specific activation time that was different then 2
minutes that was used instead. For Kappa and Q5 the protocol previously
published by Gohl and colleagues was used (Gohl et al., 2016). For
Phusion the company defined conditions were used but the same extension
time as that used for Accuprime and Platinum was used.

The 30 cycle default was used but the cycle conditions started at 15 and
increased by 5 up to 35 cycles and was used for both fecal and mock
samples. The fecal PCR consisted of all 4 samples at 15, 20, 25, 30, and
35 cycles for each Taq (total samples = 100). Although, the mock
communities also had 4 replicates used for 15, 20, 25, and 35 cycles, 10
replicates were used for 30 cycles for all Taq (total samples = 130).
For all the mock community samples there was not enough PCR product at
15 cycles for adequate sequencing.

@@

\hypertarget{ref-taq_Gohl_2016}{}
Gohl DM., Vangay P., Garbe J., MacLean A., Hauge A., Becker A., Gould
TJ., Clayton JB., Johnson TJ., Hunter R., Knights D., Beckman KB. 2016.
Systematic improvement of amplicon marker gene methods for increased
accuracy in microbiome studies. \emph{Nature Biotechnology} 34:942--949.
DOI: \href{https://doi.org/10.1038/nbt.3601}{10.1038/nbt.3601}.
